### 2016-07-01 related-work.tex

\paragraph{Reasoning under relaxed memory} Considering the
correspondences between axiomatic models of relaxed
memory~\cite{battycpp} and weakly consistent
replication~\cite{burckhardt14}, it is reasonable to expect similar
reasoning approaches to work in both the cases. Ridge~\cite{rgtso}
generalizes rely-guarantee reasoning to the x86-TSO memory model.
Likewise, Vafeadis \emph{et al.}~\cite{rsl13} generalize concurrent
separation logic (CSL)~\cite{csl} to the C11 relaxed memory model.
Ferreira \emph{et al.}~\cite{ferreira10} propose a parameterized
operational semantics for relaxed memory models, but the
parameterization is over a relation between relaxed memory programs
and related {\sc sc} programs. They also prove the soundness of CSL
for the weakest memory model expressible in their semantics, but
neither a parameterized (in the aforementioned sense) CSL, nor a CSL
specialized for any relaxed memory model is proposed.  ~\cite{DLZ+13}
presents a \emph{buffered memory model} for Java that deines an
axiomatic definition for the JMM in terms of memory reorderings, and
an operational instantiation consistent with the total store ordering
(TSO) memory model found on x86 processors, and demonstrates the
equivalence of the two definitions.  However, there is no attempt to
parameterize the model over different reordering or consistency
definitions as we demonstrate here.

>>>>

\paragraph{Reasoning under relaxed memory} Considering the
correspondences between axiomatic models of relaxed
memory~\cite{battycpp} and weakly consistent
replication~\cite{burckhardt14}, it is reasonable to expect similar
reasoning approaches to work in both the cases. Ridge~\cite{rgtso}
generalizes rely-guarantee reasoning to the x86-TSO memory model.
Likewise, Vafeadis \emph{et al.}~\cite{rsl13} generalize concurrent
separation logic (CSL)~\cite{csl} to the C11 relaxed memory model.
Ferreira \emph{et al.}~\cite{ferreira10} propose a parameterized
operational semantics for relaxed memory models, but the
parameterization is over a relation between relaxed memory programs
and related {\sc sc} programs. They also prove the soundness of CSL
for the weakest memory model expressible in their semantics, but
neither a parameterized (in the aforementioned sense) CSL, nor a CSL
specialized for any relaxed memory model is proposed.  ~\cite{DLZ+13}
presents a \emph{buffered memory model} for Java that defines an
axiomatic definition for the JMM in terms of memory reorderings, and
an operational instantiation consistent with the TSO memory model
found on x86 processors, and demonstrates the equivalence of the two
definitions.  However, there is no attempt to parameterize the model
over different reordering or consistency definitions, which is a central
focus of this paper.

### 2016-07-01 store-consistency.tex

\paragraph{Discussion.} As evident from the example, instantiating the
proof system for a specfic combination of consistency and isolation
settings, and then deriving facts specific to that setting
characterizes our reasoning approach. While intuition suggests that
some instantiations, such as {\sc sc} with ANSI SQL isolation, are
general enough to cover many practical cases, it not the case in
reality given the subtle differences in the semantics of isolation
levels among different database implementations. For instance,
Postgres' \iso{Repeatable Read} isolation is stronger than ANSI SQL's
or MySQL's in non-trivial ways.  Furthermore, the need for high
availability on geo-replicated stores has led to the development of
new isolation levels which are yet to be standardized. For example,
\emph{Parallel Snapshot Isolation}~\cite{psi} was proposed in 2011,
and \emph{Non-Monotonic Snapshot Isolation}~\cite{nmsi} in 2013, both
targeted for replicated stores. As more commercial weakly consistent
stores adopt variants of transactions, like the recently introduced
\emph{lightweight transactions} of Cassandra, it is reasonable to
expect new isolation definitions to continue to be proposed.  While it
is possible to carefully engineer a reasoning framework for each
combination of consistency and isolation, such a strategy would lead
to multiple semantic definitions and proof systems with no obvious to
compare and relate them.  Having a parameterized semantics and proof
framework built on the framework defined above allows us to support
these variants as distinct, yet comparable instantiations, thus
avoiding the need for semantics re-engineering every time an
application is retargeted to a new platform.

>>>>

\paragraph{Discussion.} As evident from the example, instantiating the
proof system for a specfic combination of consistency and isolation
settings, and then deriving facts specific to that setting
characterizes our reasoning approach. While intuition suggests that
some instantiations, such as {\sc sc} with ANSI SQL isolation, are
general enough to cover many practical cases, it not the case in
reality given the subtle differences in the semantics of isolation
levels among different database implementations. For instance,
Postgres' \iso{Repeatable Read} isolation is stronger than ANSI SQL's
or MySQL's in non-trivial ways.  Furthermore, the need for high
availability on geo-replicated stores has led to the development of
new isolation levels which are yet to be standardized. For example,
\emph{Parallel Snapshot Isolation}~\cite{psi} was proposed in 2011,
and \emph{Non-Monotonic Snapshot Isolation}~\cite{nmsi} in 2013, both
targeted for replicated stores. As more commercial weakly consistent
stores adopt variants of transactions, like the recently introduced
\emph{lightweight transactions} of Cassandra, it is reasonable to
expect new isolation definitions to continue to be proposed.  While it
is possible to carefully engineer a reasoning framework for each
combination of consistency and isolation, such a strategy would lead
to multiple semantic definitions and proof systems with no obvious way
to compare and relate them.  Having a parameterized semantics and a
proof framework built on the such semantics allows us to support these
variants as distinct, yet comparable instantiations, thus avoiding the
need for semantics re-engineering every time an
application is retargeted to a new platform.
